\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-16 papers/jfp/8-engineering.tex
Add file watching and polling section

>>>>

\subsection{File watching vs polling}\label{sec-integration-with-ides}

Most build systems use files for their inputs. When running a build, to check if a file is up-to-date, one option is to take the modification time or compute the content hash of each input file. However, for the largest projects, the mere act of checking the modification time for all the input files can become prohibitive. To overcome that problem, build systems targeted at large scale, e.g. \Bazel and \Buck, make use of file watching API's that detect when a file has changed. Using that information the build can avoid performing many file accesses.
